### 2019-07-05 2-Chapters/4-Chapter/IEEE_WCNC_2019__DemoICT.git/main.tex
Typos, and slowly updating references (old arXiv -> conf/journal version)

\begin{figure}[!h]
	\centering
    \includegraphics[height=9.0cm]{plot_datafile_append_Uniform_vs_UCB_vs_TS.eps}
    \caption[Less than $400$ communication slots (\ie, less than $100$ trials in each channel) are sufficient for the two learning devices (\UCB{} and Thompson Sampling) to reach a successful communications rate close to $80\%$, which is \textbf{twice as much} as the \textcolor{cyan}{non-learning (uniform)} device, which stays around $40\%$ of success. Similar gains of performance were obtained in other scenarios]{Less than $400$ communication slots (\ie, less than $100$ trials in each channel) are sufficient for the two learning devices (\textcolor{red}{\UCB} and \textcolor{green}{Thompson Sampling}) to reach a successful communications rate close to $80\%$, which is \textbf{twice as much} as the \textcolor{cyan}{non-learning (uniform)} device, which stays around $40\%$ of success. Similar gains of performance were obtained in other scenarios.}
    \label{fig:42:plot_datafile_append_Uniform_vs_UCB_vs_TS}
\end{figure}

>>>>

\begin{figure}[!h]
	\centering
    \includegraphics[height=9.0cm]{plot_datafile_append_Uniform_vs_UCB_vs_TS.eps}
    \caption[Less than $400$ communication slots (\ie, less than $100$ trials in each channel) are sufficient for the two learning devices (\UCB{} and Thompson Sampling) to reach a successful communications rate close to $80\%$, which is \textbf{twice as much} as the non-learning (uniform) device, which stays around $40\%$ of success. Similar gains of performance were obtained in other scenarios]{Less than $400$ communication slots (\ie, less than $100$ trials in each channel) are sufficient for the two learning devices (\textcolor{red}{\UCB} and \textcolor{green}{Thompson Sampling}) to reach a successful communications rate close to $80\%$, which is \textbf{twice as much} as the \textcolor{cyan}{non-learning (uniform)} device, which stays around $40\%$ of success. Similar gains of performance were obtained in other scenarios.}
    \label{fig:42:plot_datafile_append_Uniform_vs_UCB_vs_TS}
\end{figure}
